Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-05-03 doc/RMD/mlg-mcg.Rmd
Add MCG/MLG graph
And it is HAIRY

```{r load_packages}
library('tidyverse')
library('poppr')
library('viridis')
```

@@

```{r mlg_table, fig.width = 20, fig.height = 5}
mtab <- mlg.table(dat11, color = TRUE)
mplot <- last_plot()
mplot + scale_fill_viridis(discrete = TRUE, direction = -1, option = "C") +
  aes(color = I("black")) 
```

>>>>

```{r load_packages}
library('igraph')
library('ggraph')
library('tidyverse')
library('poppr')
library('viridis')
```

@@

```{r mlg_table, fig.width = 20, fig.height = 5, keep = "last"}
mtab <- mlg.table(dat11, color = TRUE)
mplot <- last_plot()
mplot + scale_fill_viridis(discrete = TRUE, direction = -1, option = "C") +
  aes(color = I("black")) 
```

Now we can take a look at the concordance of MLGs to MCGs

```{r}
mll.custom(dat11) <- strata(dat11)$MCG
mcgmlg <- as.data.frame(table(mll(dat11, "original"), mll(dat11, "custom"))) %>%
  setNames(c("MLG", "MCG", "Freq")) %>%
  as_data_frame() %>%
  filter(Freq > 0)
mcgs <- mcgmlg %>%
  group_by(MCG) %>%
  summarize(MLGs = sum(Freq > 0), Samples = sum(Freq), Entropy = vegan::diversity(Freq), data = list(data_frame(MLG = MLG, Freq = Freq))) %>%
  arrange(desc(MLGs))
mlgs <- mcgmlg %>%
  group_by(MLG) %>%
  summarize(MCGs = sum(Freq > 0), Samples = sum(Freq), Entropy = vegan::diversity(Freq), data = list(data_frame(MCG = MCG, Freq = Freq))) %>%
  arrange(desc(Samples), desc(MCGs))
mcgs
mlgs
any(mcgs$MLGs > 1)
```

We can see that there are plenty of MLGs that contain multiple MCGs. This

```{r}
mlg.filter(dat11, dist = bruvo.dist, replen = other(dat11)$REPLEN) <- .Machine$double.eps + (0.5/11)
dat11

fmcgmlg <- as.data.frame(table(mll(dat11, "contracted"), mll(dat11, "custom"))) %>%
  setNames(c("MLG", "MCG", "Freq")) %>%
  as_data_frame() %>%
  filter(Freq > 0)
fmcgs <- fmcgmlg %>%
  group_by(MCG) %>%
  summarize(MLGs = sum(Freq > 0), Samples = sum(Freq), Entropy = vegan::diversity(Freq), data = list(data_frame(MLG = MLG, Freq = Freq))) %>%
  arrange(desc(MLGs))
fmlgs <- fmcgmlg %>%
  group_by(MLG) %>%
  summarize(MCGs = sum(Freq > 0), Samples = sum(Freq), Entropy = vegan::diversity(Freq), data = list(data_frame(MCG = MCG, Freq = Freq))) %>%
  arrange(desc(Samples), desc(MCGs))
fmcgs
fmlgs
any(fmcgs$MLGs > 1)
```

## making a graph

I believe that making a graph to visualize this might help me understand what the h\*ck is going on.

```{r}
gdf <- mcgmlg %>% 
  mutate(MLG = paste0('MLG.', MLG))
MLGS <- gdf %>% 
  group_by(MLG) %>%
  summarize(size = sum(Freq)) %>%
  rename(vertex = MLG)
MCGS <- gdf %>% 
  group_by(MCG) %>%
  summarize(size = sum(Freq)) %>%
  rename(vertex = MCG)
VAT <- bind_rows(MLGS, MCGS)
g <- gdf %>% 
  select(MCG, MLG) %>%
  graph_from_data_frame(vertices = VAT)
osize <- V(g)$size
```

Because I have more control over the size and feel of the graph, I'm going to use
ggraph. Of course, since this IS a complicated data set, It's not going to be
very pretty to look at, but I'm going to save it as supplementary materials
because it's valuable to at least look this ugliness in the face and say, "Yeah,
I guess it's not so simple after all."

```{r, fig.width = 10, fig.height = 10}

V(g)$size <- sqrt(osize)/10
V(g)$type <- ifelse(grepl("MLG", V(g)$name), "Multilocus Genotype", "Mycelial Compatibility Group")
set.seed(2017-05-03)
lay2 <- create_layout(g, layout = "igraph", algorithm = "nicely")

mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, fill = type)) +
  geom_node_text(aes(label = gsub("MLG.", "", name), color = type, size = size/4), show.legend = FALSE) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native")), 
                 arrow = arrow(length = unit(0.0125, "native"))) +
  coord_fixed() +
  scale_color_manual(values = c("white", "black")) +
  scale_fill_manual(values = c("black", "white")) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom") +
  ggtitle("Relation of Multilocus Genotypes and MCGs")

mcg_mlg_graph
ggsave(file.path(PROJHOME, "results/figures/publication/FigureS2.svg"), 
       width = 88*3, height = 88*3, units = "mm")
```
